Supporting Information

### 2016-12-08 portfolio/text/supp.Rnw
Move dual fig 4 to supp

<<get-values, cache=FALSE, echo=FALSE>>=
load("../data-generated/output-values.rda")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
@

@@

>>>>

<<get-values, cache=FALSE, echo=FALSE>>=
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
@

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
individual permit holders \emph{within} the `r nstr` most common strategies.
Changing species diversity from year-to-year is associated with higher
variability for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with greater expected revenue
to the right of the zero line and lower expected revenue to the left of the zero
line. These effects are estimated holding fishing season length constant from
year-to-year. Dots and line segments represent medians and 50\% credible
intervals of posteriors. }
\label{fig:mirror}
\end{center}
\end{figure}
